---
title: "Preparation"
author: "E. F. Haghish"
date: "2/27/2021"
output: html_document
---

Preparation
-----------

Dynamic text is text that includes scalars obtained from R. Such a text 
paragraph obtains and interprets values from R on the fly. Here is an example:

```{r echo=FALSE}
# dropping the subject with missing grade
dropped = df[is.na(df$grade), ]
all = nrow(df)
df = df[!is.na(df$grade), ]
```

`r all` students from two school participated in the study, of which, `r nrow(dropped)` 
subject (female, age `r dropped$ageyr`) was excluded from the study because of 
her unknown grade. Both schools roughly contributed the same number of seven- and 
eight-grader subjects as you in the table below. 

_Table 1_: _Example of a __dynamic table__ _
```{r echo=FALSE, results='show'}
# did the schools contributed equally to the study?
tab1 = table(df$school, df$grade)
colnames(tab1) <- c("seven-grade", "eight-grade")
pander(tab1)
```

The table above is not necessary, but shows how easy it is to construct a table 
in R. The actual work is done by the __`pander`__ package. I will construct 
a couple of more tables in the following sections
