---
title: "Publication-Ready Data Analyis with R"
author: "E. F. Haghish"
date: "February 28, 2021"

# This is added to move the output to the ./report subdirectory
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "./report") })

output:
  word_document:
    toc: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# increase the resolution of the figures to make them publication-ready
# At least, the DPI should be 300 
knitr::opts_chunk$set(dpi=600,fig.width=7)
```

In this document I will demonstrate how to create and organize a computational 
project and how to produce a dynamic document as you are developing the 
data analysis. 

Producing such a document within R might appear to be tedious at the first 
glance. But it is not, if you you make yourself familiar with the Rmarkdown workflow. On the bright side, 
a data analysis developed in these manners is transparent and easy to 
comprehend and inspect. The project is also easy to share, improving the practice of 
collaboration on data analysis. 

The data analysis is organized in several Rmd files. The **`MAIN.Rmd`** file 
execute them all within a single document. For the following example, I use a data set 
from the `lavaan` package: <https://lavaan.ugent.be/tutorial/cfa.html>. 

- The analysis is carried out using `R version 3.5.1` on `Mac OSX version 10.14.6` 
- The following R packages are also required:
  + `pander v. 0.6.3` 
  + `lavaan v. 0.6.7.` 
  + `psych v. 2.0.12`
  + `semPlot v. 1.1.2`

```{r, include=FALSE}
# EXAMIN the packages installed in your machine
libraries = c("pander","lavaan","psych","semPlot")
for (i in libraries) print(paste(i, "package version is", packageVersion(i)))
```


```{r include=FALSE}
# load the data and the required packages
library(lavaan)
library(pander)
library(psych)
library(semPlot)
df = readRDS("./data/HolzingerSwineford1939.rds")
```

Results
=======

```{r eval=TRUE, child = 'code/preparation/01_preparation.Rmd'}
```

```{r eval=TRUE, child = 'code/descriptive/01_descriptive.Rmd'}
```

```{r eval=TRUE, child = 'code/analysis/01_analysis.Rmd'}
```

---

### Last words

Preparing this project took only a few hours of work. I didn't do much of an 
analysis here, but the template is ready to be used for a real project. 
Therefore, practicing data analysis in this manner is neither unrealistic nor 
time-consuming. It's just a matter of habit. 

Once you practice your data analysis with such a discipline, it becomes easy to 
follow and review your logic for planning and conducting the data analysis. 
And that is a step forward to reproducible research. As a final word, I want to 
point out that the majority of the R code and its output was excluded in the 
MS Word. This is also what happens in the actual scientific papers, i.e. only the 
absolute-necessary outputs are included in the manuscript. Therefore, 
a dynamic document like this indeed profides the full picture of the process of 
data analysis. 






